---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ussie

<!-- badges: start -->
[![R-CMD-check](https://github.com/zoews/ussie/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/zoews/ussie/actions/workflows/R-CMD-check.yaml)
[![test-coverage](https://github.com/zoews/ussie/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/zoews/ussie/actions/workflows/test-coverage.yaml)
<!-- badges: end -->

Here is a sample package created at the 2022 Tidy Tools Workshop in Washington, DC! We will standardize and transform European football (soccer) data to compare across messy datasets. This is a way to practice using the package development tooling in R.

## Installation

You can install the development version of ussie from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("zoews/ussie")
```

## Example

Here is an example using Spain's European Football data.

```{r example}
library(ussie)
spain <- uss_make_matches(engsoccerdata::spain, "Spain")
summary(spain)

```

### Get matches

Here is a way to get matches
```{r matches_example}
library(ussie)
spain <- uss_get_matches("spain")
summary(spain)

```
